Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/workload.tex
beginning to work out the so misleading case

\textbf{Other misleading RLA results.}

>>>>

\textbf{Misleading SO Risk Measures.} As we consider the idea of misleading samples, it is noteworthy that SO \BRAVO suffers from a different and unique type of misleading result.

After drawing $n>1$ ballots in a round, some number $k$ of them are votes for the announced winner. There are $\binom{n}{k}$ possible sequences of ballots which can lead to such a sample. Given the value of $k$, however, the particular sequence of the sample contains no additional information about whether the sample is more likely under one the alternative or null hypotheses.
That said, an SO \BRAVO RLA will not stop as a function of $n$ and $k$ but also as a function of the sequence. In particular, if the sequence of ballots is such that the standard \BRAVO stopping condition was met for some $n'<n$ and corresponding $k'<n$, the audit will stop, even if by the end of the sequence the values $k$ and $n$ no longer meet the \BRAVO condition. To be clear, this is not a mathematical issue; stopping in such cases is still a correct application of Wald's SPRT result. The misleading nature of such stoppages is the note we are making.

It is easy to use our simulations to see how often this occurs.
